\vspace{-1.5cm}\normalsize{\textbf{Fairly Random: Impact of Winning the Toss on the Probability of Winning}}

### 2015-09-04 write_up/cricket.tex
Removed duplication of scripts, edited readme
Adding bib

In nearly all cricket matches, it is claimed that there is a clear advantage to bowling (batting) first. The advantage is pointed to by commentators, by team captains in the pre-toss interview, and by the captain of the losing team in the post-match interview. This isn't to say that there is actually an advantage to winning the toss. For it may be impossible to predict well in advance the advantage of bowling or batting first. Or it may be that teams squander the potential advantage by using bad heuristics to choose what they do.

@@

Data are from 43,185 first-class men's cricket matches.\footnote{You can find the scripts used to scrape the data, the final data set, and scripts used for analysis at: \href{http://github.com/soodoku/get-cricket-data/}{http://github.com/soodoku/get-cricket-data/}.} It is a near census of the relevant population. We have data on all types of matches: domestic and international Twenty20s -- T20 and T20I respectively, domestic and international one-dayers -- List A and One-Day Internationals (ODI) respectively, and domestic and international multi-day matches -- First Class (FC) and Tests respectively.\footnote{There is a rich variety of first-class matches. In English county cricket, first-class matches last four days. Some first class matches last just a day. Others two days. Yet others three days. And till a particular point in history, a test match lasted as long as it was needed to finish a game. We elide over such differences.}

@@

A caveat about interpretation before we discuss the results. As we allude to at the start, it is hard, if not impossible, to distinguish between lack of advantage of winning a toss and not capitalizing on the potential advantage.

@@

>>>>

In nearly all cricket matches, it is claimed that there is a clear advantage to bowling (batting) first. The advantage is pointed to by commentators, by team captains in the pre-toss interview, and by the captain of the losing team in the post-match interview. This isn't to say that there is actually an advantage to winning the toss, or that in lies in what is claimed, or that teams are able to successfully exploit it. For it may be impossible to predict well in advance the advantage of bowling or batting first. Or it may be that teams squander the potential advantage by using bad heuristics to choose what they do.

@@

\citep{de1998winning}, \citep{dawson2009bat}, \url{http://www.slate.com/articles/sports/sports_nut/2010/11/flipping_awesome.html}

\section*{Data}
Data are from 43,185 first-class men's cricket matches.\footnote{You can find the scripts used to scrape the data, the final data set, and scripts used for analysis at: \href{http://github.com/soodoku/get-cricket-data/}{http://github.com/soodoku/get-cricket-data/}.} It is a near census of the relevant population. We have data on all types of matches: domestic and international Twenty20s -- T20 and T20I respectively, domestic and international one-dayers -- List A and One-Day Internationals (ODI) respectively, and domestic and international multi-day matches -- First Class (FC) and Tests respectively.\footnote{There is a rich variety of first-class matches. In English county cricket, first-class matches last four days. Some first class matches last just a day. Others two days. Yet others three days. And till a particular point in history, a test match lasted as long as it was needed to finish a game. We elide over such differences.}

@@

\section*{Results}
A caveat about interpretation before we discuss the results. As we allude to at the start, it is hard, if not impossible, to distinguish between lack of advantage of winning a toss and not capitalizing on the potential advantage.

@@

\clearpage
\bibliographystyle{apsr}
\bibliography{luckybib}
